Verifying Demonstrations

### 2018-11-20 paper/privacy-properties.tex
Removes old stuff we've settled on

Coercion resistance is not possible to achieve for protests.
For instance, someone could simply physically bring Alice to a protest against her will.
%Seb: ok but if Alice can refuse to upload her participation proof then coercion resistance can still be achieved
Receipt freeness, while appealing at first glance, is not desirable in our context, as in contrast to voting, receipt freeness for \emph{how} the voter voted (\ie the cause of the protest) implies receipt freeness for \emph{that} the voter voted (\ie the protester was there), which conflicts with verifiability.
\daniel{%
  No, that implication is not true, counter example:
  There is receipt freeness for how an elector voted, but not that they voted.
  As Simon pointed out, they tick me off, so it's visible that I've voted.
  But no one will ever know for which party I voted.%
}

\daniel{%
  This doesn't conflict with verifiability either.
  I keep track of the ballot box, as long as that and all ballots inside are 
  treated properly, I know my ballot is safe and counted.%
}

\daniel{%
  In our case:
  I have a key issued on a smartcard and it is tied to my identity.
  If the hardware corrupts itself after issuing the \ac{NIZK} proof, then there 
  is no way to check whether I created \(\pid = \ACprf[_k][\cid]\) or \(\pid' = 
    \ACprf[_k][\cid']\).
  I could have downloaded both from the ledger.
  But I know which is mine, I can submit it, and as long as the block where it 
  was included is intact I know my proof-share is included as well --- even if 
  I forget what it looked like.%
}

Thus, in our context the crucial property is therefore privacy.
More precisely for the protester, we want unlinkability between a protester's real identity \(P\) and the cause identifier \(\cid\) against the adversary.
Given a participation proof, Grace should not be able to distinguish if it belongs to Alice or Bob.
Furthermore, if Grace has managed to link one proof to Alice due to some auxiliary knowledge, she should not be able to link it to another proof (\eg, from a different protest).

>>>>

Coercion resistance is not possible to achieve for protests.
For instance, someone could simply physically bring Alice to a protest against her will.
Receipt freeness, while appealing at first glance, is not desirable\footnote{%
  Or not possible without violating some of the verifiability 
  requirements.
} in our context since this will conflict with verifiability: in contrast to 
voting, receipt freeness for \emph{how} the voter voted (\ie the cause of the 
protest) implies receipt freeness for \emph{that} the voter voted (\ie the 
protester was there), which conflicts with verifiability.

Thus, in our context the crucial property is therefore privacy.
More precisely, for the protester we want unlinkability (from the adversary's 
perspective) between a protester's real identity \(P\) and the cause identifier 
\(\cid\).
Phrased differently, given a participation proof, Grace should not be able to 
distinguish if it belongs to Alice or Bob.
Furthermore, if Grace has managed to link one proof to Alice due to some 
auxiliary knowledge, she should not be able to link it to another proof (\eg 
from a different protest).
